The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-18 methods/ms.tex
claudia's corrections

@@

All of the SCUBA 850 and 450 \mum\ data has been re-processed in a uniform
manner and made publicly available as the SCUBA Legacy Catalog
\citep[][hereafter SLC]{difrancesco08}.  These maps provide an excellent
cross-check on the accuracy of the BGPS pointing model.  We have used the same
cross-correlation procedure as that used to obtain the relative alignment of
Bolocam observations to compare to the SLC.  A number of concerns might arise
in comparing the Bolocam to the SCUBA maps, including the differing scan
strategies (SCUBA maps were typically taken in jiggle-map mode, which tends to
remove extended structure) and the often restricted range of positions measured
within an extended cloud for the SLC.  The cross-correlation technique actually
mitigates these effects, since it does not require the establishment of a
single position for an object (which may differ due to the change in wavlength
between the surveys or due to the observing strategy) but rather makes use of
all the information available.  The morphological correlation between SCUBA and
BGPS sources is generally excellent with some exceptions, giving a high degree
of confidence to the comparison and to the results obtained from the pointing
model.  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
find that the RMS offset between BGPS and SLC positions within a $3\arcdeg
\times 1\arcdeg$ block defined by the BGPS is $4.0\pm8.8$\arcsec, consistent
with the errors derived for the Bolocam pointing model.  There were some BGPS
fields that had larger offsets from SCUBA fields; these fields were excluded
from the offset measurement above because of poor morpohological match.

@@

% 8
% -----------------------------------------------------------------------------
\FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
distribution of absolute reference sources (crosses) in the Galactic
Plane (Appendix \ref{app:PointingCalibrators}).  Also shown (crosses)
are the locations of bright, isolated, compact sources for comparison
with other surveys, as given in Appendix \ref{app:ReferenceSources}.
Right: The distribution of the pointing calibration sources across the
local sky in Hawaii during the July 2007 epoch when the pointing model
was constructed.  Note the good sampling built up over the range of
sky observed in the Survey.}{fig:PointingCalibrators}{1.0}
% -----------------------------------------------------------------------------

% 9
% -----------------------------------------------------------------------------
\begin{figure}
  \subfigure[The pointing model correction (left) and residuals (right) for
  Epoch V, from which the master reference images were derived for subsequent
  alignment.  The red line indicates the fitted model. 510 pointing sources
  were included, and the final RMS was 5.77\arcsec in altitude and 3.21\arcsec
  in azimuth, or a total RMS offset of 6.6\arcsec]
{\label{fig:PointingModel-a}\includegraphics[scale=0.9]{paper_models_0707}}\\

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution. ($\sigma = 5.94,2.92$)]
{\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}

@@

The essential signal-processing problem to be solved by the mapping
algorithm is the estimation and removal of a signal due to fluctuating
atmosphere emission which is $>\sim$100's of times stronger than the typical
sources in our maps.  We implement an iterative procedure for
estimating both the atmosphere fluctuations and the astrophysical
signal without {\it a priori} knowledge of either.

@@

To further remove the atmosphere (and other correlated instrument
noise) without a detailed physical model, we use principal component
analysis (PCA) as given in \citet{laurent05}.

@@

\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the PSD
    of the data.  The second harmonic of 60 Hz is aliased via beating against
    the 130 Hz bolometer bias frequency into 10 Hz with sidebands split at
    $\sim1$ Hz.  It is removed by replacing components at these frequencies in
    the fourier transform with gaussian noise matched to the local mean
    amplitude.

@@

Due to the large volume of data generated by the survey, it was
necessary to develop new tools to quickly visualize the data and
ensure data quality.  A common tool in radio astronomy is the
so-called ``waterfall'' plot, which is an image with frequency on the
x-axis, time on the y, and an intensity proportional to the
interferometer visibility amplitude or phase.  We have used a variant
on this to visualize the Bolocam data by displaying bolometer number
(related to the bolometer position in the focal plane) on the x-axis
and time on the y, with the intensity given by the bolometer's
response (in Jy) at that time.  An example of this is shown in Figure
\ref{fig:Flagger}.  With practice, anomalies such as the glitch shown
can be detected and manually and iteractively flagged out.

An automated flagger was also created that flags out outlier data on a
per-pixel basis.  In order to make a robust measurement of the
variance of the fluxes assigned to each pixel, we used the median
average deviation (MAD) over the data in the pixel and rejected high and low
outliers at the 3-sigma level.  Pixels with too little data to compute
a deviation, i.e. those with $<3$ data points, were also flagged out -
these scan-edge pixels are the dominant contribution to the total
number of flagged data points.

@@

% -----------------------------------------------------------------------------
\setcounter{subfig}{1}
\begin{figure}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_withglitch}
    \end{center}
  \end{minipage}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_glitchgone}
    \end{center}
  \end{minipage}
  \caption{An illustration of the flagging process using the waterfall plot.
  Left: The glitch apparent at middle right (bolometer 98, around 6.2s) is the
  same one whose time series is shown in Figure \ref{fig:Flagger}b.  Because of
  the PCA subtraction, the effect of the glitch also propagates over the other
  bolometers, appearing as a horizontal stripe. Right: The same data displayed
  with the time point including the glitch flagged out and rescaled}

@@

%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
%the flagging process using the waterfall plot. Left: The glitch
%apparent at middle right is the same one whose time series is shown in
%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
%effect of the glitch also propagates over the other bolometers,
%appearing as a horizontal stripe. Right: The same data displayed with
%the time point including the glitch flagged out and rescaled}
%{fig:Flaggin}{1.0}
%
\Figure{crs}{The distribution of glitch amplitudes flagged and removed from the
data in the \lon=111 field.  Glitches below the detection threshold may
contribute to the overall noise.}{fig:GlitchDistribution}{1.0}

@@

\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
on the iterative process can be seen in its effect on the
residuals. From left to right: map, noise, model. Top to
bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
has the result of leaving no flux in the residual at the location of
Sgr B2, and does not ``dig a hole'' in the residual map, as the
7.2\arcsec\ kernel does.  The 7.2\arcsec\ kernel also lacks the
noise-rejection features of the larger kernels, as can be seen in the
last panel.}{fig:Deconvolution}{1.0}

@@

The residual maps produced by the iterative mapping provide a natural way of
estimating the systematic error resulting from imperfect subtraction of bright
sources.  The imperfect subtraction results in ``ghosts'' of the bright sources
in the error maps $E$.

Residual maps are produced for each map from the residuals after
removing the astrophysical signal model and the PCA atmosphere model.  These
maps are useful for diagnosing the effect of the iterative process on bright
sources and as a method of obtaining an
estimate of the noise.

@@

The depth can be converted into an
estimate of mass via standard estimates, i.e., under the assumption of
a temperature, opacity, and distance.
Using dust opacity from \citet{ossenkopf94}
%\citet{enoch06} and \citet{young06},
and assuming a gas-to-dust mass ratio 100, the mass sensitivity
can be written as
\begin{equation} 
\label{eq:Mass}
M_{gas}\approx
0.22\left( e^{13.1/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
D^{2}_{kpc} \msol 
\end{equation}
where $D_{kpc}$ is the distance to the source in kpc.  (At $S_\nu =
15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
13$~K, so for $T_d > 10$K the dependence is approximately linear.  At
the coldest temperatures expected, the mass changes a factor of 2.9
between 20 and 10 K.  The distance to the clump is more important in most
situations.

\Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
function of Galactic longitude.  Black is the standard deviation of
$0.9\arcdeg \times 0.9\arcdeg$ degree blocks centered on $b=0$ and the
longitude indicated for the error maps $E$; red is similar, but the
estimator is median(1/sqrt(weight map).}{fig:NoiseVsLongitude}{1.0}

\section{Effect of the Analysis on Photometry}
\label{sec:Photometry}

To do accurate and meaningful photometry on the Bolocam maps requires
a good estimate of the noise (Section \ref{sec:Noise}) but also an
understanding of the spatial filtering imposed by the observing
strategy and the cleaning and mapping of the data.  Quite apart from
the issues discussed in this section are the issues of identifying
sources with complex morphology and defining the regions over which to
do the aperture.  This is discussed in \citet{rosolowsky09}.  Here we
merely deal with the limitations on performing photometry imposed by
the data itself.

The Bolocam maps produced are the convolution of the (nearly Gaussian)
primary beam $G(\xad)$, together with an effective high-pass
spatial filter $F(\xad)$ (figure \ref{fig:PCA_filter}),
\[
M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
\]

@@

To assess the effect of the mapping algorithm, we performed a series
of simulations.

Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in
the map as a function of source size for a range of different PCA
components subtracted in the cleaning.  These measurements were
produced by inserting simulated gaussian sources at a range of peak
flux densities and sizes spread out through the map and summing the
flux in an ellipse on the final cleaned map. Real data with the
astrophysical source model removed were used as the background.

@@

\FigureTwo{pca_comparison_nolegend_l111}{deconvolution_comparison_nolegend_l111}{The
fractional flux recovered as a function of source size for
well-separated Gaussian sources with the FWHM as indicated.
\emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
(teal), 26 (lime), 31 (black) PCA components subtracted.  
Note that flux recovery drops to 50\% at 120\arcsec for the 13 PCA
component cleaning used in the released data.  The 3 and 7 PCA cases
show bumps because atmospheric noise is still present at large scales.
The $>$100\% recovery for sources smaller than the deconvolution kernel is a
side-effect; since the deconvolution kernel is smaller than the beam, no real
source should ever be smaller than the kernel.
\emph{Right}:
7.2\arcsec (cyan), 14.4\arcsec (black), 21.6\arcsec (red), 31.2\arcsec (green)
deconvolution kernel for 13 PCA components subtracted.  It is clear that the
larger deconvolution kernels generate spurious signal at smaller scales, but
the flux recovery is very close to 1 at the beam size
(35\arcsec)}{fig:PCA_Filter}{1.0}

\Figure{aper_phot_hpf_beam}{The effect of performing aperture
photometry on a point source of unit flux observed with the effective
Bolocam PSF $B$.  The black curve shows the area (measured in pixels)
as a function of the aperture radius for the filter measured via
simulation.  This is compared to the equivalent case for a Gaussian
beam (green).  The vertical lines show radii of $n/2 \times FWHM$ for
$n=1,2,3$.  One can see that the Gaussian beam has nearly reached a
constant area of $2 \pi \sigma^2$ by a radius of $3/2 \times FWHM$, at
which point any larger aperture would recover the full flux of the
source.  The actual Bolocam beam reaches its maximum effective area
sooner, and then drops precipitously as the size of the aperture is
increased.  }{fig:ESF}{1.0}

@@

All processed maps are made available through
IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
IPAC provides a cutout service for the images as well as a searchable
version of the catalog provided in \citep{rosolowsky09}.  The full
release includes
\begin{enumerate}
\item Calibrated maps for all regions observed (MAP)
% don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
\item The deconvolved MAP (DECONVMAP)
\item Maps of integration time per pixel (NHITSMAP)
\item Maps of noise per pixel (NOISEMAP)
\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP)
\end{enumerate}

@@

>>>>

\addtocounter{figure}{-1}
\addtocounter{subfig}{1}

@@

All SCUBA 850 and 450 \mum\ data has been re-processed in a uniform
manner and made publicly available as the SCUBA Legacy Catalog
\citep[][hereafter SLC]{difrancesco08}.  These maps allow a 
cross-check of the accuracy of the BGPS pointing model.  We have applied the same
cross-correlation procedure used to obtain the relative alignment of
BGPS observations to compare the BGPS images to the SLC.  Concerns might arise
in comparing the Bolocam to the SCUBA maps, such as the differing scan
strategies (SCUBA maps were typically taken in jiggle-map mode, which tends to
remove extended structure).  The cross-correlation technique actually
mitigates these effects, since it does not require the establishment of a
single position for an object (which may differ due to the change in wavelength
between the surveys or due to the observing strategy) but rather makes use of
all the information available.  The by-eye morphological comparison between SCUBA and
BGPS sources is generally excellent with some exceptions, giving a high degree
of confidence to the comparison and to the results obtained from the BGPS pointing
model [include Di Francesco pointing accuracy].  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
find that the RMS offset between BGPS and SLC positions within a $3\arcdeg
\times 1\arcdeg$ block defined by the BGPS is $4.0\pm8.8$\arcsec, consistent
with the errors derived for the Bolocam pointing model.  There were some BGPS
fields that had larger offsets from SCUBA fields; these fields were excluded
from the offset measurement above because of poor morpohological match.

@@

% 8
% -----------------------------------------------------------------------------
\FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
distribution of absolute reference sources (crosses) in the Galactic
Plane (Appendix \ref{app:PointingCalibrators}).  Also shown (crosses)
are the locations of bright, isolated, compact sources for comparison
with other surveys, as given in Appendix \ref{app:ReferenceSources}.
Right: The distribution of the pointing calibration sources across the
local sky in Hawaii during July 2007 (epoch V) when the pointing model
was constructed.  }{fig:PointingCalibrators}{1.0}
% -----------------------------------------------------------------------------

% 9
% -----------------------------------------------------------------------------
\begin{figure}
  \subfigure[The pointing model correction (left) and residuals (right) for
  Epoch V, from which the master reference images were derived for subsequent
  alignment.  The red line indicates the fitted model. 510 pointing sources
  were included, and the final RMS was 5.77\arcsec in altitude and 3.21\arcsec
  in azimuth, or a total RMS offset of 6.6\arcsec.  No systematic offset with
  altitude was found.]
{\label{fig:PointingModel-a}\includegraphics[scale=0.9]{paper_models_0707}}\\

  \subfigure[The residuals of the pointing model.  The Gaussian fits have
  $\sigma = 5.94,2.92$ in altitude offset and azimuth offset respectively.]
{\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}

@@

The essential signal-processing problem to be solved by the mapping
algorithm is the estimation and removal of a signal due to fluctuating
atmospheric emission which is $>\sim$100's of times stronger than the typical
sources in our maps.  We implement an iterative procedure for
estimating both the atmosphere fluctuations and the astrophysical
signal without {\it a priori} knowledge of either.

@@

To further remove the atmosphere (and other correlated instrument
noise) without a detailed physical model, we use principal component
analysis (PCA) as given in \citet{laurent05}. [more words]

The mean across each scan is forced to zero by subtracting a polynomial
fit to the scan after iteratively rejecting astrophysical sources.  This
process helps reduce negative bowls in the scan direction near bright sources.

@@

\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the power spectral density (PSD)
    of the data.  The second harmonic of 60 Hz is aliased via beating against
    the 130 Hz bolometer bias frequency into 10 Hz with sidebands split at
    $\sim1$ Hz.  It is removed by replacing components at these frequencies in
    the fourier transform with gaussian noise matched to the local mean
    amplitude.

@@

Due to the large volume of data generated by the survey, it was
necessary to develop new tools to quickly visualize the data and
ensure data quality.  A common tool in radio astronomy is the
so-called ``waterfall'' plot, which is an image with frequency on the
x-axis, time on the y, and an intensity proportional to the
interferometer visibility amplitude or phase.  We have used a variant
on this to visualize the Bolocam data by displaying bolometer number
(related to the bolometer position in the focal plane) on the x-axis
and time on the y, with the intensity given by the bolometer's
response (in Jy) at that time.  An example of this is shown in Figure
\ref{fig:Flagger}.  Anomalies such as the glitch shown
can be detected and manually and interactively flagged out.

An automated flagger was also created that flags out outlier data on a
per-map-pixel basis.  In order to make a robust measurement of the
variance of the fluxes assigned to each pixel, we used the median
average deviation (MAD) over the data in the pixel and rejected high and low
outliers at the 3-sigma level.  Pixels with too little data to compute
a deviation, i.e. those with $<3$ data points, were also flagged out -
these scan-edge pixels are the dominant contribution to the total
number of flagged data points.

@@

% -----------------------------------------------------------------------------
\setcounter{subfig}{1}
\begin{figure}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_withglitch}
    \end{center}
  \end{minipage}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_glitchgone}
    \end{center}
  \end{minipage}
  \caption{An illustration of the flagging process using the waterfall plot.
  Left: The glitch apparent at middle right (bolometer 98, around 6.2s) is the
  same one whose time series is shown in (\em{b}).  Because of
  the PCA subtraction, the effect of the glitch also propagates over the other
  bolometers, appearing as a horizontal stripe. Right: The same data displayed
  with the time point including the glitch flagged out and rescaled}

@@

%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
%the flagging process using the waterfall plot. Left: The glitch
%apparent at middle right is the same one whose time series is shown in
%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
%effect of the glitch also propagates over the other bolometers,
%appearing as a horizontal stripe. Right: The same data displayed with
%the time point including the glitch flagged out and rescaled}
%{fig:Flaggin}{1.0}
%
\Figure{crs}{The distribution of glitch amplitudes flagged and removed from the
data in the \lon=111 field.  Glitches below the detection threshold may
contribute to the overall noise.  Each data point represents .1s of integration
time.}{fig:GlitchDistribution}{1.0}

@@

\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution on the
iterative process can be seen in its effect on the residuals in these images of
Sgr B2, all displayed at the same scale. From left to right: map, residual,
model. Top to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which has the
result of leaving no flux in the residual at the location of Sgr B2, and does
not ``dig a hole'' in the residual map, as the 7.2\arcsec\ kernel does.  The
7.2\arcsec\ kernel also lacks the noise-rejection features of the larger
kernels, as can be seen in the last panel.}{fig:Deconvolution}{1.0}

@@

The residual maps produced by the iterative mapping provide a natural way of
estimating the systematic error resulting from imperfect subtraction of bright
sources.  The imperfect subtraction results in positive ``ghosts'' of the
bright sources in the error maps $E$.  Smoothed residual maps also provide the
best means of determining the pixel-to-pixel error near bright sources.  Near
the scan edges, 1/sqrt(weightmap) provides a better estimate of the local noise.

% Residual maps are produced for each map from the residuals after
% removing the astrophysical signal model and the PCA atmosphere model.  These
% maps are useful for diagnosing the effect of the iterative process on bright
% sources and as a method of obtaining an
% estimate of the noise.

@@

[since we don't do any science in this paper, should this be held off for
use in Erik's paper?]
The depth can be converted into an
estimate of mass via standard estimates, i.e., under the assumption of
a temperature, opacity, and distance.
Using dust opacity from \citet{ossenkopf94}
%\citet{enoch06} and \citet{young06},
and assuming a gas-to-dust mass ratio 100, the mass sensitivity
can be written as
\begin{equation} 
\label{eq:Mass}
M_{gas}\approx
0.22\left( e^{13.1/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
D^{2}_{kpc} \msol 
\end{equation}
where $D_{kpc}$ is the distance to the source in kpc.  (At $S_\nu =
15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
13$~K, so for $T_d > 10$K the dependence is approximately linear.  At
the coldest temperatures expected, the mass changes a factor of 2.9
between 20 and 10 K.  The distance to the clump is more important in most
situations.

\Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
function of Galactic longitude.  The black histogram plots the standard deviation as a 
function of longitude binned in $0.9\arcdeg \times 0.9\arcdeg$ degree blocks
(to avoid high-noise regions at scan edges) centered on $b=0$ for the error
maps $E$.  Red is similar, but the estimator is median(1/sqrt(weight
map).}{fig:NoiseVsLongitude}{1.0}

\section{Effects of the Data Reduction Procedures on Photometry}
\label{sec:Photometry}

To do accurate and meaningful photometry on the Bolocam maps requires
a good estimate of the noise (Section \ref{sec:Noise}) but also an
understanding of the spatial filtering imposed by the observing
strategy and the cleaning and mapping of the data.  
The additional
complexities of defining ``sources'' in complicated regions are discussed in
\citet{rosolowsky09}.  Here we restrict our discussion to the limitations
on performing photometry imposed by the data reduction.

The BGPS maps are the convolution of the (nearly Gaussian)
primary beam $G(\xad)$ and an effective high-pass
spatial filter $F(\xad)$ (figure \ref{fig:PCA_filter}),
\[
M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
\]

@@

To assess the effect of the mapping algorithm, we performed a series
of simulations.  Gaussian sources with a range of peak flux densities and sizes
were inserted on top of a background consisting of real BGPS data with the
astrophysical source model removed.  The recovered fluxes were measured in
ellipses that included single well-separated sources.  Figure
\ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
function of source size for a range of different PCA components subtracted in
the cleaning.

@@

\FigureTwo{pca_comparison_nolegend_l111}{deconvolution_comparison_nolegend_l111}{The
fractional flux recovered as a function of source size for
well-separated Gaussian sources with FWHM as indicated.
\emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
(teal), 26 (lime), 31 (black) PCA components subtracted.  
Note that flux recovery drops to 50\% at 120\arcsec for the 13 PCA
component cleaning used in the released data.  The 3 and 7 PCA cases
show bumps because atmospheric noise is still present at large scales.
The $>$100\% recovery for simulated sources smaller than the deconvolution kernel is a
side-effect; since the deconvolution kernel is smaller than the beam, no real
astrophysical source should ever be smaller than the kernel.
\emph{Right}:
7.2\arcsec (cyan), 14.4\arcsec (black), 21.6\arcsec (red), 31.2\arcsec (green)
deconvolution kernel for 13 PCA components subtracted.  It is clear that the
larger deconvolution kernels generate spurious signal at smaller scales, but
the flux recovery is very close to 1 at the beam size
(35\arcsec)}{fig:PCA_Filter}{1.0}

\Figure{aper_phot_hpf_beam}{[James - figure needs clarification] The effect of performing aperture
photometry on a point source of unit flux observed with the effective
Bolocam PSF $B$.  The black curve shows the area (measured in pixels)
as a function of the aperture radius for the filter measured via
simulation.  This is compared to the equivalent case for a Gaussian
beam (green).  The vertical lines show radii of $n/2 \times FWHM$ for
$n=1,2,3$.  One can see that the Gaussian beam has nearly reached a
constant area of $2 \pi \sigma^2$ by a radius of $3/2 \times FWHM$, at
which point any larger aperture would recover the full flux of the
source.  The actual Bolocam beam reaches its maximum effective area
sooner, and then drops precipitously as the size of the aperture is
increased.  }{fig:ESF}{1.0}

@@

All processed maps are available through
IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
IPAC provides a cutout service for the images as well as a searchable
version of the catalog provided in \citet{rosolowsky09}.  The full
release includes
\begin{enumerate}
\item Calibrated maps for all regions observed (MAP)
% don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
\item The deconvolved MAP (MODEL)
\item Maps of integration time per pixel (NHITSMAP)
\item Maps of residual noise per pixel (RESIDUAL)
\item Maps of inverse variance per pixel (WEIGHTMAP)
\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP) \citep{rosolowsky09}
\end{enumerate}

@@

\bf{Claudia suggested that this section be removed or changed to an `advertisement' section
where we indicate what follow-up work needs to be done - seems reasonable, since this
is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}
